---
title: "Additional functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Additional functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE
)
```

```{r setup}
library(cardinalR)
```

The function `gen_nsum(n, k)` divides a total sum `n` into `k` positive integers. It first assigns an equal base value to each element and then randomly distributes any remainder, ensuring the elements sum exactly to `n`.

```{r, echo=TRUE}
gen_nsum(n = 100, k = 3)
```

The function `gen_nproduct(n, p)` aims to produce `p` positive integers whose product is approximately `n`. It starts with all elements equal to the rounded $p^{th}$ root of `n` and iteratively adjusts elements up or down in a randomized manner until the product is within a small tolerance of `n`. This accommodates the fact that exact integer solutions for a given product are often impossible.

```{r, echo=TRUE}
gen_nproduct(n = 500, p = 4)
```
